ms_figures

### 2023-01-06 ms_figures.Rmd

# Create basic plot for the legend
# artis_region_method %>%
#   group_by(year, exporter_region) %>%
#   summarise(live_weight_t = sum(live_weight_t)) %>%
#   ggplot(aes(x = year, y = live_weight_t, fill = exporter_region)) +
#   geom_area() +
#   scale_fill_manual(values = region_colors) +
#   labs(fill = "Region") +
#   theme(legend.position = "bottom")
```

>>>>

# Create basic plot for the legend

# artis_region_method %>%
#   group_by(year, exporter_region) %>%
#   summarise(live_weight_t = sum(live_weight_t)) %>%
#   ggplot(aes(x = year, y = live_weight_t, fill = exporter_region)) +
#   geom_area() +
#   scale_fill_manual(values = region_colors) +
#   labs(fill = "Region") +
#   theme(legend.position = "bottom")
```
